Figures to insert in text

### 2018-03-01 Chapters/sdm2.tex

>>>>

\begin{figure}[ht!]
  \centering
  \subfloat[]{\includegraphics[width=2.4in]{./images02/new-images/qn3.png}}
  \subfloat[]{\includegraphics[width=2.4in]{./images02/new-images/qn7.png}}

  \subfloat[]{\includegraphics[width=4.2in]{./images02/new-images/qn10.png}}

  \caption{Graph $Q_n$, for $n \in$ \{3, 7, 10\}. Each node represents a possible bitstring in $\{0,1\}^N$, and two nodes are linked if the bitstrings differ by a single dimension.  A number of observations can be made here. First, the number of nodes grows as $2^N$ as N grows; which makes use of the entire space infeasible as $N>>20$. Another interesting observation, better seen in the figures below, is that most of the space lies at the center, at a distance of around 500 from any given vantage point. Though Kanerva has derived many combinatorial properties of the space, I believe that this is a aesthetically appealing object on its own, and beautiful results can be found in the graph-theoretical literature.\label{The hypercube is also studied in graph theory.}}
  \end{figure}

%FOOTNOTE:

Here is an interesting question that I leave for further research: A hypercube with n dimensions can be divided by two hypercubes with $n-1$ dimensions. Is there an algorithm that separates the area of each hard-location in such a form that there exists a function mapping each bitstring in $\{0,1\}^N$ to the set of hard locations it belongs to?  In other words… though this would break Kanerva's assumption of a uniformly distributed set of hard locations for a perfectly symmetrical set of hard locations, there could be large performance gains if such a mapping function from a bitstring to its corresponding set of nearest hard locations exists.

%  (See \cite{@article{harary1988survey,
%    title={A survey of the theory of hypercube graphs},
%    author={Harary, Frank and Hayes, John P and Wu, Horng-Jyh},
%    journal={Computers \& Mathematics with Applications},
%    volume={15},
%    number={4},
%    pages={277--289},
%    year={1988},
%    publisher={Elsevier}
%  }}
